\ttitle

### 2013-12-09 Chapters/Chapter6.tex
WIP
WIP: Working on organization of Chapter 2

\input{./Chapters/Chapter6/data_gathering}

>>>>

This chapter discusses the real-world data sets used for this research.
In \Cref{sec:data_sets} we discuss earlier used data sets and argue that these are inappropriate for our research.
It is followed by an overview of the setup we have created to record continuous data sets from an uncontrolled environment, both in- and outdoor.
The activities performed are discussed in \Cref{sec:data_gathering}.
As discussed in \Cref{Chapter4}, the algorithm is subject to user parameters.
In \Cref{sec:real_world_parameters} the effect and ranges of the parameters on the real world data sets are discussed.
Finally, the performance of the algorithm is discussed in \Cref{sec:real_world_performance}.

\input{./Chapters/Chapter6/data_sets}
\input{./Chapters/Chapter6/data_gathering}
\input{./Chapters/Chapter6/parameters}
\input{./Chapters/Chapter6/performance}

### 2013-12-09 Chapters/Chapter6/data_gathering.tex
WIP

% !TEX root = ../../main.tex
\section{Data Gathering}\label{sec:data_gathering}

\TODO{Use common data sets. The WISDM dataset is not useful because it has no transitions, only very clear blocks of the same activities. Include a plot to illustrate the problem?}

\begin{figure}\label{fig:wisdm_excerpt}
\centering
  \includegraphics[width=1\textwidth]{./Figures/Chapter6/data_collection/wisdm_excerpt.eps}
  \caption[WISDM Excerpt]{Excerpt from the WISDM data set \cite{kwapisz2011activity}. First five activities for subject $33$ are displayed. Due to the discontinuous nature of the recordings, this data set can not be used for change detection.}
\end{figure}

\begin{figure}\label{fig:uci_annotated}
\centering
  \includegraphics[width=1\textwidth]{./Figures/Chapter6/data_collection/uci_annotated.eps}
  \caption[UCI HAR Excerpt]{Excerpt from the UCI HAR data set \cite{anguita2012human}. The recorded training activities for subject $25$ are displayed. Due to the imprecise (and possibly incorrect) labeling and the short duration of activities, the data set can not be used for the change detection method as described in this thesis.}
\end{figure}

%---- Run 1: walk-run-roemer
\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/chapter6/data_collection/run-1-walk-run-roemer/data_plot_rot_annotated.eps}
  \caption[R1: rotation]{Run 1: Walk-run-roemer, rotation}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/chapter6/data_collection/run-1-walk-run-roemer/data_plot_mag_annotated.eps}
  \caption[R1: mag]{Run 1: Walk-run-roemer, Mag}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/chapter6/data_collection/run-1-walk-run-roemer/data_plot_acc_annotated.eps}
  \caption[R1: accelerometer]{Run 1: Walk-run-roemer, accelerometer}
\end{figure}

%---- Run 2: walk-run-jos
\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/chapter6/data_collection/run-2-walk-run-jos/data_plot_rot_annotated.eps}
  \caption[R2: rotation]{Run 2: Walk-run-jos, rotation}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/chapter6/data_collection/run-2-walk-run-jos/data_plot_mag_annotated.eps}
  \caption[R2: mag]{Run 2: Walk-run-jos, Mag}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/chapter6/data_collection/run-2-walk-run-jos/data_plot_acc_annotated.eps}
  \caption[R2: accelerometer]{Run 2: Walk-run-jos, accelerometer}
\end{figure}

@@

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/chapter6/data_collection/stills/jos_cp_walk-run.png}
  \caption[Recording still 1]{Subject 1 on the transition from walking to running}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/chapter6/data_collection/stills/jos_run_2.png}
  \caption[Recording still 2]{Subject 1 running}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/chapter6/data_collection/stills/jos_run.png}
  \caption[Recording still 3]{Subject 1 running}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/chapter6/data_collection/stills/jos_sprint.png}
  \caption[Recording still 4]{Subject 1 sprinting}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/chapter6/data_collection/stills/jos_walking.png}
  \caption[Recording still 5]{Subject 1 walking}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/chapter6/data_collection/stills/roemer_run_cw.png}
  \caption[Recording still 6]{Subject 2 running in clockwise corner}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/chapter6/data_collection/stills/roemer_walk.png}
  \caption[Recording still 7]{Subject 2 walking}
\end{figure}

>>>>

% !TEX root = ../../main.tex
\section{Data Gathering}\label{sec:data_gathering}
For our data sets of real world activities we have sampled both in- and outdoor activites.
The subjects performing the activities are three males, in an age around 25.
We have used two series of recordings.
The first series are various outdoor recordings with segments of walking, running and standing.
Some movement activities are performed in a straight line, whilst others are performed around corners of in a wide circular direction.
The second series consist of mainly walking up and down the stairs, with small vertical parts between the segments.
The stairs are all in a circular shape.

\subsection{Outside}\label{subsec:outside}

\TODO{For each data set: discovered timepoint with acc, mag, rot, and all combined. Use closest change point}

\begin{center}\begin{table}
  \begin{tabulary}{\textwidth}{|c|c|c|}
    \hline
    \multicolumn{3}{|c|}{Subj 1, run 1} \\
    \hline \hline
    Act. & Ann. & Disc. \\
    \hline
    Still & 0 & *0* \\
    \hline
    Shake & 3.5 & *3.5* \\
    \hline
    Still & 4.2 & *4.2* \\
    \hline
    In pocket & 5.5 & *5.5* \\
    \hline
    Walk & 7 & *7* \\
    \hline
    Run & 10 & *10* \\
    \hline
    Walk & 14 & *14* \\
    \hline
    Run & 17.2 & *17.2* \\
    \hline
    Walk & 22.1 & *22.1* \\
    \hline
    Turn CCW & 23.5 & *23.5* \\
    \hline
    Walk & 24.2 & *24.2* \\
    \hline
    Run (sprint) & 28 & *28* \\
    \hline
    Run & 31 & *31* \\
    \hline
    Walk & 33 & *33* \\
    \hline
    Run & 35.5 & *35.5* \\
    \hline
    Walk & 39 & *39* \\
    \hline
    Out pocket & 41 & *41* \\
    \hline
    Still & 43 & *43* \\
    \hline
  \end{tabulary}
  \caption[Performed activities subject 1 run 1]{The outdoor series performed activities by subject 1, run 1.}
  \label{tab:outdoor_series}
\end{table}\end{center}

\begin{center}\begin{table}
  \begin{tabulary}{\textwidth}{|c|c|c|}
    \hline
    \multicolumn{3}{|c|}{Subj 2, run 1} \\
    \hline \hline
    Act. & Ann. & Disc. \\
    \hline
    Still & 0 & *0* \\
    \hline
    Shake & 4 & *4* \\
    \hline
    Still & 5 & *5* \\
    \hline
    In pocket & 8.8 & *8.8* \\
    \hline
    Walk & 12 & *12* \\
    \hline
    Run & 16 & *16* \\
    \hline
    Walk & 21.3 & *21.3* \\
    \hline
    Run & 24.5 & *24.5* \\
    \hline
    Walk & 28.3 & *28.3* \\
    \hline
    Turn CCW & 30 & *30* \\
    \hline
    Walk & 31.8 & *31.8* \\
    \hline
    Run & 32.8 & *32.8* \\
    \hline
    Walk & 37 & *37* \\
    \hline
    Run (sprint) & 39.5 & *39.5* \\
    \hline
    Run & 42 & *42* \\
    \hline
    Walk & 44.5 & *44.5* \\
    \hline
    Out pocket & 49.5 & *49.5* \\
    \hline
    Still & 52 & *52* \\
    \hline
    Shake & 55.7 & *55.7* \\
    \hline
    Still & 56.8 & *56.8* \\
    \hline
  \end{tabulary}
  \caption[Performed activities subject 2 run 1]{The outdoor series performed activities by subject 2, run 1.}
  \label{tab:outdoor_series}
\end{table}\end{center}

\TODO{Replace all times in the stars with the closest discovered change point}

%---- Run 1: walk-run-roemer
\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/chapter6/data_collection/run-1-walk-run-roemer/data_plot_rot_annotated.eps}
  \caption[R1: rotation]{Run 1: Walk-run-roemer, rotation}
  \label{fig:data_gathering_run_1_rot}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/chapter6/data_collection/run-1-walk-run-roemer/data_plot_mag_annotated.eps}
  \caption[R1: mag]{Run 1: Walk-run-roemer, Mag}
  \label{fig:data_gathering_run_1_mag}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/chapter6/data_collection/run-1-walk-run-roemer/data_plot_acc_annotated.eps}
  \caption[R1: accelerometer]{Run 1: Walk-run-roemer, accelerometer}
  \label{fig:data_gathering_run_1_ann}
\end{figure}

%---- Run 2: walk-run-jos
\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/chapter6/data_collection/run-2-walk-run-jos/data_plot_rot_annotated.eps}
  \caption[R2: rotation]{Run 2: Walk-run-jos, rotation}
  \label{fig:data_gathering_run_2_rot}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/chapter6/data_collection/run-2-walk-run-jos/data_plot_mag_annotated.eps}
  \caption[R2: mag]{Run 2: Walk-run-jos, Mag}
  \label{fig:data_gathering_run_2_mag}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/chapter6/data_collection/run-2-walk-run-jos/data_plot_acc_annotated.eps}
  \caption[R2: accelerometer]{Run 2: Walk-run-jos, accelerometer}
  \label{fig:data_gathering_run_2_ann}
\end{figure}

%---- Run 3: Stairs remco
\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/chapter6/data_collection/stairs-1-marc/data_plot_rot_annotated.eps}
  \caption[R3: rotation]{Run 3: Indoor stairs Marc, rotation}
  \label{fig:data_gathering_run_3_rot}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/chapter6/data_collection/stairs-1-marc/data_plot_mag_annotated.eps}
  \caption[R3: mag]{Run 3: Indoor stairs Marc, Mag}
  \label{fig:data_gathering_run_3_mag}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/chapter6/data_collection/stairs-1-marc/data_plot_acc_annotated.eps}
  \caption[R3: accelerometer]{Run 3: Indoor stairs Marc, accelerometer}
  \label{fig:data_gathering_run_3_ann}
\end{figure}

@@

Stills from subject 3:

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/chapter6/data_collection/stills/jos_cp_walk-run.png}
  \caption[Recording still 1]{Subject 1 on the transition from walking to running}
  \label{fig:data_gathering_still_1_still_walk_to_run}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/chapter6/data_collection/stills/jos_run_2.png}
  \caption[Recording still 2]{Subject 1 running}
  \label{fig:data_gathering_still_1_running}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/chapter6/data_collection/stills/jos_run.png}
  \caption[Recording still 3]{Subject 1 running}
  \label{fig:data_gathering_still_1_running_2}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/chapter6/data_collection/stills/jos_sprint.png}
  \caption[Recording still 4]{Subject 1 sprinting}
  \label{fig:data_gathering_still_1_sprint}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/chapter6/data_collection/stills/jos_walking.png}
  \caption[Recording still 5]{Subject 1 walking}
  \label{fig:data_gathering_still_1_walk}
\end{figure}

Stills from subject 2:

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/chapter6/data_collection/stills/roemer_run_cw.png}
  \caption[Recording still 6]{Subject 2 running in clockwise corner}
  \label{fig:data_gathering_still_2_run}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/chapter6/data_collection/stills/roemer_walk.png}
  \caption[Recording still 7]{Subject 2 walking}
  \label{fig:data_gathering_still_2_walk}
\end{figure}

Stills from subject 3:

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/chapter6/data_collection/stills/marc_downstairs.png}
  \caption[Recording still 8]{Subject 3 descencing the stairs.}
  \label{fig:data_gathering_still_3_descending}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/chapter6/data_collection/stills/marc_stairs_up_walk.png}
  \caption[Recording still 9]{Subject 3 will start walking for a small fragment and will continue ascending the stairs.}
  \label{fig:data_gathering_still_3_ascending}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/chapter6/data_collection/stills/marc_walk.png}
  \caption[Recording still 10]{Subject 3 walking in the hallway. He will turn $180^{\circ}$ counter-clockwise.}
  \label{fig:data_gathering_still_3_walk}
\end{figure}
